Titeln på avhandlingens språk

### 2023-02-13 body/part1/overview/methodology.tex
cleave done?

\todo[inline]{Discuss, at high level, the advantages of this methodology for NCSs.
Refer back to related work. }

>>>>

We discuss an initial case study of our methodology in the context of \glspl{NCS} and similar \glspl{CPS} in \cref{paper:olguinmunoz2022cleave}.
In this work, we present \gls{CLEAVE}, a software-based framework for scalable and repeatable benchmarking of edge-native \aclp{NCS}.
The growing adoption of edge computing has made it important to understand the strengths and weaknesses of different edge concepts for the deployment of such \glspl{CPS}.

\gls{CLEAVE} is a fully virtualized benchmarking framework, inspired by our previous work in \cref{paper:olguinmunoz2018demoscaling,paper:olguinmunoz2019edgedroid} on benchmarking human-in-the-loop applications on the edge.
In the case of \gls{CLEAVE} however, we forgo the trace-based approach of EdgeDroid in favor of direct modeling of the target systems.
\gls{CLEAVE} includes a benchmarking framework and software development kit for the development of emulated physical systems and softwarized controllers.
These virtual \glspl{CPS} can then be deployed on real networks for reparametrizable, repeatable, and reproducible benchmarking.

\gls{CLEAVE} is built using Python 3.8, making it highly extensible and able to use existing libraries.
It is compatible with container technologies such as Docker~\cite{docker}, making it suitable for automated deployment, scaling, and benchmarking on industry-standard edge setups using container orchestration solutions.

\begin{figure}
    \centering
    \includegraphics[width=.9\textwidth]{publications/2022CLEAVE/images/CLEAVE_experiment_setup}
    \caption{
        The setup used for experimentation in the \gls{NCS} case study.
        Figure originally published in \cref{paper:olguinmunoz2022cleave}.
    }\label{fig:cleavesetup}
\end{figure}

We study the validity of our methodology and the implementation of the software framework through a simple scenario, illustrated in \cref{fig:cleavesetup}.
An inverted pendulum plant controlled by a proportional-differential controller is deployed on an Edge server over a Wi-Fi link, while video-streaming applications run concurrently on the setup.
The inverted pendulum is a popular benchmark in control-system literature, and the setup allows for straightforward reparametrization and a broad range of experiments.
Video analytics, on the other hand, is a main proposed use case for edge computing, and it is likely that edge \gls{NCS} deployments will be deployed in parallel with such applications in the future.
Using Wi-Fi allows for more experimental freedom, as the system can be adapted to study both best-case and worst-case scenarios with low and high latencies, respectively.

We first establish a baseline by deploying a single control loop.
This setup is repeated multiple times with different sampling rates to obtain statistically significant results.
The results of the single-loop scenarios show, as expected, that higher sampling rates tend to correlate with better quality of control and that network delays can be compensated for by increasing the sampling rate.

\begin{figure}[t]
    \centering
    \begin{subfigure}[t]{.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{publications/2022CLEAVE/plots/fixed_video_topple_frac}
        \caption{Fraction of experimental runs with at least one toppled plant.}%\label{paper:olguinmunoz2022cleave:fig:video:toppled}
    \end{subfigure}%
    \hfill%
    \begin{subfigure}[t]{.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{publications/2022CLEAVE/plots/fixed_video_rtt}
        \caption{\glspl{RTT}.}%\label{paper:olguinmunoz2022cleave:fig:video:rtt}
    \end{subfigure}%
    \caption{
        Results from experimentation with multiple \gls{CLEAVE} control loops co-deployed with video streaming applications.
        Error bars indicate \SI{95}{\percent} \glspl{CI} in all plots.
        Figures originally published in \cref{paper:olguinmunoz2022cleave}.
    }\label{fig:cleaveresults}
\end{figure}

Next, we study the interaction between the control systems and the video-streaming applications.
Six control loops are deployed, as uplink \gls{UDP} traffic from four clients is generated to emulate the load generated by Full-HD video streaming.
Based on the baseline results, we execute scenarios with varying plant sampling rates and repeat each scenario \num{30} times.
Representative results from this experimentation are showcased in \cref{fig:cleaveresults}.
While the baselines might lead us to think that higher sampling rates are always better for the stability of control systems, the results from these experiments show that network and resource contention are important factors when designing \glspl{NCS} for deployment on the edge.
As sampling rates increase, a critical point is eventually reached at which the congestion on the network link is such that it severely impacts the quality of control.
We conclude that adaptive sampling might be thus a viable method for optimizing resource utilization in these systems.

The results of the experiments will be useful for optimizing resource utilization in edge-bound networked control systems.
The results of the experiments with video-streaming applications will add to the understanding of the interaction between control systems and networked applications.
Furthermore, the success of our experimentation shows that our methodology, implemented through \gls{CLEAVE}, makes the repeated experimentation and data collection convenient compared to fully physical setups, while at the same time providing enhanced realism with respect to simulated approaches.
